### 2017-11-08 README.Rmd
Update pkgdown

```
install.packages("devtools")
devtools::install_github("andrewbpray/infer")
```

@@

## Hypothesis tests
![](figs/ht-diagram.png)

@@

Check the package vignettes for further examples using theory-based methods
in combination with randomization-based methods.

>>>>

```
install.packages("devtools")
devtools::install_github("andrewpbray/infer")
```

@@

## Hypothesis tests
![](https://github.com/andrewpbray/infer/blob/master/figs/ht-diagram.png)

@@

Check the package vignettes for further examples using theory-based methods
in combination with randomization-based methods. The examples below only show the calculation of randomization-based statistics. Check the vignettes for ways to `visualize()` these statistics.
